An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-22 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational and physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the operating environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering 
of services and applications for CPS~\cite{Metzger2014}. Software pervasiveness in CPS places 
new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.

@@

\textcolor{red}{In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.}

@@

During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability \textcolor{red}{~\cite{Alsadi2018}}. The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand. A reliable power is a generation system that has sufficient power to feed load demand in a period.

@@

The NPC or life-cycle cost is the present value of all the costs over the project lifetime, 
minus the present value of all the revenues that it earns over the project lifetime. 
The net present worth is found by discounting all cash inflows and outflows, 
including cost of installation, replacement and maintenance of the PV system, 
at an internal rate of return (IRR)~\cite{Park2004}.  IRR is used to evaluate the attractiveness of a project or investment.

@@

Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: $20$ years;
	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}. This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries). Therefore, it will be performed three battery bank replacements during the LCC analysis.
\end{itemize}

@@

Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 
perform off-grid system with battery backup analysis. 
Additionally, HOMER and RETScreen include economical analysis 
or even optimization-sensitive analysis. Therefore, in this study, 
HOMER Pro will be the simulation tool used to compare with our automated synthesis method. 
Note that that HOMER Pro is available only for Microsoft Windows and 
its annual standard subscription costs US\$ $504.00$ ~\cite{HOMER}.

@@

We have performed seven stand-alone PV system case studies 
to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification). 
These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. 
%
\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro \\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & XYZ \\
\hline
\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:2$\times$320W (2S)\\NBT:2$\times$80Ah (2S)\\Controller 40A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,133.39} & XYZ \\
\hline
\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & XYZ \\
\hline
\makecell{\textbf{Case Study 4}\\Demand:253W\\Peak:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & XYZ \\
\hline
\makecell{\textbf{Case Study 5}\\Demand:263W\\Peak:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & XYZ \\
\hline
\makecell{\textbf{Case Study 6}\\Demand:322W\\Peak:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & XYZ \\
\hline
\makecell{\textbf{Case Study 7}\\Demand:1,800W\\Peak:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & XYZ \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}. During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.

@@

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.

@@

During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}. The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand. A reliable power is a generation system that has sufficient power to feed load demand in a period.

@@

The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime. The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.  IRR is used to evaluate the attractiveness of a project or investment.

@@

Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: $20$ years;
	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}. This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every 10 years). Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
\end{itemize}

@@

Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis. Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis. Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.  Related to HOMER Pro:

\begin{itemize}
	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases. However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the 365 days of the year;
	\item HOMER Pro do not have a explicit equipment called charge controller. It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}. During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component. With that in mind, it was included a generic flat plate PV of 1kW and generic lead-acid batteries of 1kW as well (and with capacity of 83.4 Ah according with HOMER Pro modeling). HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
\end{itemize}

@@

We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification). These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. 
%
\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}
